An empirical assessment of strategies to model opponent effects in crash severity analysis

### 2020-06-06 Interactions-Crash-Severity/Response-to-Reviewers-v3.Rmd

---
title: "Response to reviewers"
author: ""
date: "6/6/2020"
output: pdf_document
---

We wish to thank three anonymous reviewers for their feedback on the second version of our paper. In this letter we respond to their comments and describe the changes made to the paper in response. Reviewer comments are in black and our responses in blue.

@@

\newpage

# Reviewer 1

No comment to authors.

>\textcolor{blue}{Thank you for reading the paper again.}

This paper is very well done and the revisions have improved it even further.

>\textcolor{blue}{Thank you for your suggestions to improve the paper.}

1. Authors mentioned that the WAPE are still less than one percent for every model/ensemble of models in Table 6. This is true. But it does not change the fact that the models are overfitting. If you evaluate the model performances based on other criteria, the in-sample and out-of-sample performances might be quite different. As such, these models might be biased.

2. I’m very confused by the calculation process of “percent correct”. Not sure if it is a proper performance measure. As the authors mentioned, that crash data is highly imbalanced. In this case, there are other performance metrics which are more adapted into imbalanced data problem, such as ROC, G-mean, or F-measure. You can refer to the following paper

Learning from class-imbalanced data: Review of methods and applications

https://www.sciencedirect.com/science/article/pii/S0957417416307175

>>It is curious that its ‘percent correct by class’ is generally very high (close to or greater than 90%) when numbers are so bad; it is curious too that the ‘percent correct’ is always lower than the lowest value of each ‘percent correct by class’.

### 2020-06-06 Interactions-Crash-Severity/Cover-Letter-v1.Rmd
Changed name of folder with paper before working on revisions for v3

Please find attached our jointly authored submission entitled "An empirical assessment of strategies to model opponent effects in crash severity analysis". We wish to submit this paper for publication consideration in Analytical Methods in Accident Research.

@@

It is our hope that you will find the topic of the research to be a good fit to Analytical Methods in Accident Research, and that your expert reviewers will be able to provide valuable feedback to improve our research.

>>>>

Please find attached our jointly authored submission entitled "An empirical assessment of strategies to model opponent effects in crash severity analysis". We wish to submit this paper for publication consideration in Accident Analysis & Prevention.

@@

It is our hope that you will find the topic of the research to be a good fit to Accident Analysis & Prevention, and that your expert reviewers will be able to provide valuable feedback to improve our research.

### 2020-06-06 Interactions-Crash-Severity/Interactions-Crash-Severity-Title-Page-v1.tex
Changed name of folder with paper before working on revisions for v3

% Pandoc header
\usepackage[margin=1in]{geometry}

@@

  \title{An empirical assessment of strategies to model opponent effects in crash
severity analysis}
    \author[]{Antonio Paez\corref{Corresponding Author}}
   \ead{paezha@mcmaster.ca} 
    \author[Louisiana State University]{Hany Hassan}
   \ead{hassan1@lsu.edu} 
    \author[McMaster University]{Mark Ferguson}
   \ead{fergumr@mcmaster.ca} 
    \author[McMaster University]{Saiedeh Razavi}
   \ead{razavi@mcmaster.ca} 
      \address[McMaster University]{McMaster Institute for Transportation and Logistics, 1280 Main Street
West, Hamilton, Ontario, Canada L8S 4K1}
    \address[Louisiana State University]{Department of Civil and Environmental Engineering, Baton Rouge,
Louisiana, USA 70803}

  \begin{abstract}
  Road accidents impose an important burden on health and the economy.
  Numerous efforts to understand the factors that affect road collisions
  have been undertaken. One stream of research focus on modelling the
  severity of crashes. Crash severity research is useful to clarify the
  way different factors can influence the outcome of the event. The
  objective of this paper is to assess different strategies to model the
  interactions between participants in a crash, in the context of crashes
  involving two parties. Towards this objective, a series of models are
  estimated using data from Canada's National Collision Database. Three
  levels of crash severity (no injury/injury/fatality) are analyzed using
  ordered logit models and covariates for the participants in the crash
  and the conditions of the crash. Modelling strategies include different
  ways of introducing the covariates (e.g., in a single-level or
  multi-level form), as well as by subsetting the dataset. The models are
  assessed using predicted shares and outcomes, and the results highlight
  the importance of considering opponent effects in crash severity
  analysis. On the other hand, the study suggests that hierarchical (i.e.,
  multi-level) specifications and subsetting do not perform necessarily
  better than a relatively simple single-level model with opponent
  effects.
  \end{abstract}

>>>>

% Pandoc header
\usepackage[margin=1in]{geometry}
\usepackage{lineno}
\linenumbers

@@

  \title{An empirical assessment of strategies to model opponent effects in crash
severity analysis}
    \author[McMaster University]{Antonio Paez\corref{Corresponding Author}}
   \ead{paezha@mcmaster.ca} 
    \author[Louisiana State University]{Hany Hassan}
   \ead{hassan1@lsu.edu} 
    \author[McMaster University]{Mark Ferguson}
   \ead{fergumr@mcmaster.ca} 
    \author[McMaster University]{Saiedeh Razavi}
   \ead{razavi@mcmaster.ca} 
      \address[McMaster University]{McMaster Institute for Transportation and Logistics, McMaster
University, 1280 Main Street West, Hamilton, Ontario, Canada L8S 4K1}
    \address[Louisiana State University]{Department of Civil and Environmental Engineering, Louisiana State
University, Baton Rouge, Louisiana, USA 70803}

  \begin{abstract}
  Road accidents impose an important burden on health and the economy.
  Numerous efforts to understand the factors that affect road collisions
  have been undertaken. One stream of research focus on modelling the
  severity of crashes. Crash severity research is useful to clarify the
  way different factors can influence the outcome of an event. The
  objective of this paper is to assess different strategies to model the
  interactions between participants in a crash in the context of crashes
  involving two parties. Towards this objective, a series of models are
  estimated using data from Canada's National Collision Database. Three
  levels of crash severity (no injury/injury/fatality) are analyzed using
  ordered logit models and covariates for the participants in the crash
  and the conditions of the crash. Modelling strategies include different
  ways of introducing the covariates (e.g., in a single-level or
  multi-level form), as well as by subsetting the dataset. The models are
  assessed using predicted shares and classes of outcomes, and the results
  highlight the importance of considering opponent effects in crash
  severity analysis. The study also suggests that hierarchical (i.e.,
  multi-level) specifications and subsetting do not necessarily perform
  better than a relatively simple single-level model with opponent
  effects. The results of this study provide insights regarding the
  performace of different modelling strategies, and should be informative
  to researchers working with crash severity models.
  \end{abstract}

### 2020-06-06 Interactions-Crash-Severity/Interactions-Crash-Severity-v1.tex
Changed name of folder with paper before working on revisions for v3

  \title{An empirical assessment of strategies to model opponent effects in crash
severity analysis}
    \author[Some University]{Author 1\corref{Corresponding Author}}
   \ead{author1@address.edu} 
    \author[Another University]{Author 2}
   \ead{author2@address.edu} 
      \address[Some University]{Address}
    \address[Another University]{Address}

@@

\begin{quote}
\textbf{Note:} this paper presents reproducible research. The source
file is an R Markdown document. All code and data necessary to reproduce
the analysis are available from the following anonymous Drive folder:
\end{quote}

\begin{quote}
https://drive.google.com/open?id=12aJtVBaQ4Zj0xa7mtfqxh0E48hKCb\_XV
\end{quote}

\begin{quote}
The source files, code, and data will be publicly available in a GitHub
repository upon acceptance of the paper for publication
\end{quote}

>>>>

  \title{An empirical assessment of strategies to model opponent effects in crash
severity analysis}
    \author[McMaster University]{Antonio Paez\corref{Corresponding Author}}
   \ead{paezha@mcmaster.ca} 
    \author[Louisiana State University]{Hany Hassan}
   \ead{hassan1@lsu.edu} 
    \author[McMaster University]{Mark Ferguson}
   \ead{fergumr@mcmaster.ca} 
    \author[McMaster University]{Saiedeh Razavi}
   \ead{razavi@mcmaster.ca} 
      \address[McMaster University]{McMaster Institute for Transportation and Logistics, McMaster
University, 1280 Main Street West, Hamilton, Ontario, Canada L8S 4K1}
    \address[Louisiana State University]{Department of Civil and Environmental Engineering, Louisiana State
University, Baton Rouge, Louisiana, USA 70803}

@@

\begin{quote}
\textbf{Note:} this paper presents reproducible research. The source
file is an R Markdown document. All code and data necessary to reproduce
the analysis are available from the following GitHub repository:
\end{quote}

\begin{quote}
https://github.com/paezha/Modelling-Participant-Interactions-in-Crash-Severity
\end{quote}
